---
title: "Data poor validation" 
subtitle: "Myers data"
author: "Laurence Kell"
output: rmarkdown:::word_document
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
tags: FLPKG FLR
license: Creative Commons Attribution-ShareAlike 4.0 International
---
  
```{r knitr_init, echo=FALSE, results="hide"}
library(knitr)
## Global options
opts_chunk$set(echo    =FALSE,
               eval    =TRUE,
               cache   =TRUE,
               cache.path="../cache/myers/",
               prompt  =FALSE,
               comment =NA,
               message =FALSE,
               tidy    =FALSE,
               warning =FALSE,
               fig.height=6,
               fig.width =6,
               fig.path  ="../tex/myers-",
               dev       ="png")

options(digits=3)

iFig=0
```

```{r, pkgs, echo=FALSE, message=FALSE}
library(reshape)
library(plyr)
library(dplyr)
library(ggplot2)

library(sraplus)
```

```{r, data, fig.height=6, fig.width=6}
load("/home/laurence-kell/Desktop/rfmo/iccat/sc-eco/iccat/jabba/jabbaiccat.RData")

jabbaiccat=jabbaiccat[sort(names(jabbaiccat))]

spp=c("Thunnus obesus",
      "Kajikia albida",
      "Xiphias gladius",
      "Makaira nigricans",
      "Thunnus albacares")
names(spp)=names(jabbaiccat)
jb=ldply(jabbaiccat,function(x)
       data.frame(year=x$timeseries$year,b=x$timeseries$ssb,b_div_bmsy=x$timeseries$ssb/x$refpts$bmsy[1]))
names(jb)[1]="sp"
```


```{r, db, eval=FALSE}
bds=mlply(data.frame(sp=names(spp)), function(sp){

  x=jabbaiccat[[sp]]
  
  cdp<-try(sraplus::format_driors(
    use_heuristics=!TRUE,
    taxa          =spp[sp],
    
    index      = x$timeseries$ssb,
    index_year = x$timeseries$year,
    catch      = x$timeseries$catch,
    years      = x$timeseries$year
    ))
  
  fit<-try(sraplus::fit_sraplus(
    driors = cdp,      
    engine = "tmb",
    model  = "sraplus_tmb",
    estimate_qslope = FALSE,
    estimate_proc_error = TRUE))

  if ("try-error"%in%is(fit)) return(NULL)
  
  fit})

save(bds,file="/home/laurence-kell/Desktop/papers/data-poor/results/jabbaBDResults.RData")
```


```{r, db4, eval=FALSE}
bd4=mlply(data.frame(sp=names(spp)), function(sp){

  x=jabbaiccat[[sp]]
  
  set.seed(1234)
  
  cdp<-try(sraplus::format_driors(
    use_heuristics=!TRUE,
    taxa          =spp[sp],
    
    index      = x$timeseries$ssb*rev(rlnorm(length(x$timeseries$ssb),0,0.4)),
    index_year = x$timeseries$year,
    catch      = x$timeseries$catch,
    years      = x$timeseries$year
    ))
  
  fit<-try(sraplus::fit_sraplus(
    driors = cdp,      
    engine = "tmb",
    model  = "sraplus_tmb",
    estimate_qslope = FALSE,
    estimate_proc_error = TRUE))

  if ("try-error"%in%is(fit)) return(NULL)
  
  fit})

save(bd4,file="/home/laurence-kell/Desktop/papers/data-poor/results/jabbaBD4Results.RData")
```

```{r, sra, eval=FALSE}
sras=mlply(data.frame(sp=names(spp)), function(sp){
  
  x=jabbaiccat[[sp]]
  
  cdp<-try(sraplus::format_driors(
    use_heuristics=TRUE,
    taxa          =spp[sp],
    
    catch      = x$timeseries$catch,
    years      = x$timeseries$year
  ))
  
  
  fit<-try(sraplus::fit_sraplus(
    driors = cdp,
    engine = "sir",
    adapt_delta = 0.9,
    max_treedepth = 10,
    n_keep = 4000,
    chains = 1,
    cores = 1,
    estimate_qslope = FALSE,
    estimate_proc_error = TRUE))
  
  if ("try-error"%in%is(fit)) return(NULL)
  
  fit})

save(sras,file="/home/laurence-kell/Desktop/papers/data-poor/results/jabbaSRAResults.RData")
```


```{r, srap, eval=FALSE}
srap=mlply(data.frame(sp=names(spp)), function(sp){
  
  print(sp)
  print(spp[sp])
  
  x=jabbaiccat[[sp]]
  r=x$pfunc[,"r"]
  k=x$pfunc[,"k"]
  p=x$pfunc[,"p"]
  
  cdp<-try(sraplus::format_driors(
    use_heuristics=!TRUE,
    taxa          =spp[sp],
    catch         =x$timeseries$catch,
    years         =x$timeseries$year,
    
    shape_prior       =p+1,
    growth_rate_prior =r,
    k_prior           =k,
    initial_state     =0.75, #x$timeseries$ssb[1]/x$refpts[1,"k"],
    terminal_state    =0.2, #x$timeseries$ssb[length(x$timeseries$ssb)]/x$refpts[1,"k"],

    k_prior_cv          =0.3,
    growth_rate_prior_cv=0.3,
    shape_prior_cv      =0.3,
    initial_state_cv    =0.3,
    terminal_state_cv   =0.5
  ))
  
  fit<-try(sraplus::fit_sraplus(
    driors = cdp,
    engine = "sir",
    adapt_delta = 0.9,
    max_treedepth = 10,
    n_keep = 4000,
    chains = 1,
    cores = 1,
    estimate_qslope = FALSE,
    estimate_proc_error = TRUE))
  
  if ("try-error"%in%is(fit)) return(NULL)
  
  fit})

save(srap,file="/home/laurence-kell/Desktop/papers/data-poor/results/jabbaSRPResults.RData")
```

```{r, eval=FALSE}
library(fishmethods)
source('~/Desktop/flr/fishmethods/R/catchmsy.R', echo=TRUE)

cmsy=mlply(data.frame(sp=names(spp)), function(sp){
  
  print(sp)
  print(spp[sp])
  
  
  x=jabbaiccat[[sp]]
  r=x$pfunc[,"r"]
  k=x$pfunc[,"k"]
  p=x$pfunc[,"p"]
  
  catch = x$timeseries$catch
  year   = x$timeseries$year

  fit<-catchmsy(
      year   =year,
      catch  =catch,
      catchCV=NULL,
      catargs=list(dist="none",low=0,up=Inf,unit="MT"),
      l0=list(low=0.75, #max(1,min(x$timeseries$ssb[1]/x$refpts[1,"k"],1),
              up =0.75, #min(x$timeseries$ssb[1]/x$refpts[1,"k"],1),
              step=0),
      lt=list(low  =0.1, #rev(x$timeseries$ssb)[1]/x$refpts[1,"k"]*0.5,
              up   =0.5, #rev(x$timeseries$ssb)[1]/x$refpts[1,"k"]*2.0,
              refyr=max(x$timeseries$year)),sigv=0,
      k=list(dist="unif",low=k*.1,up=k*10,mean=0,sd=0),
      r=list(dist="unif",low=r*.2,up=r*2,mean=0,sd=0),
      M=list(dist="unif",low=0.2,up=0.2,mean=0.00,sd=0.00),
      nsims=30000,
      graphs=NULL)

  fit})

save(cmsy,file="/home/laurence-kell/Desktop/papers/data-poor/results/jabbaCMSYResults.RData")
```

```{r}
load("/home/laurence-kell/Desktop/papers/data-poor/results/jabbaBDResults.RData")
load("/home/laurence-kell/Desktop/papers/data-poor/results/jabbaBD4Results.RData")  
load("/home/laurence-kell/Desktop/papers/data-poor/results/jabbaSRAResults.RData")
load("/home/laurence-kell/Desktop/papers/data-poor/results/jabbaSRPResults.RData")
load("/home/laurence-kell/Desktop/papers/data-poor/results/jabbaCMSYResults.RData")  

bd=ldply(bds,function(x){
  if (is.null(x)) return(NULL)
  subset(x$results,variable%in%c("b_div_bmsy","b"))})

bd4=ldply(bd4,function(x){
  if (is.null(x)) return(NULL)
  subset(x$results,variable%in%c("b_div_bmsy","b"))})

sra=ldply(sras,function(x){
  if (is.null(x)) return(NULL)
  subset(x$results,variable%in%c("b_div_bmsy","b"))})

srp=ldply(srap,function(x){
  if (is.null(x)) return(NULL)
  subset(x$results,variable%in%c("b_div_bmsy","b"))})

cmsy.bmsy=ldply(cmsy,function(x){
  dt=cbind(x$timeseries,bmsy=rep(x$Values$Bmsy,rep=length(unique(x$timeseries$year))))
  ddply(dt, .(flag,year), with, quantile(value/bmsy,probs=c(0.975,0.945,0.5,0.045,0.025)))
  })
names(cmsy.bmsy)[c(5:7)]=c("upper","mean","lower")

cmsy.b=ldply(cmsy,function(x){
  dt=cbind(x$timeseries,bmsy=rep(x$Values$Bmsy,rep=length(unique(x$timeseries$year))))
  ddply(dt, .(flag,year), with, quantile(value,probs=c(0.975,0.945,0.5,0.045,0.025)))
  })
names(cmsy.b)[c(5:7)]=c("upper","mean","lower")

dat=rbind.fill(cbind(Model="Catch & Index",        bd),
               cbind(Model="Catch & Index Error",  bd4),
               cbind(Model="Catch & Heuristics",   sra),
               cbind(Model="Catch & Priors",       srp),
               cbind(Model="CMSY",           subset(cmsy.b,   flag==1),variable="b"),
               cbind(Model="CMSY",           subset(cmsy.bmsy,flag==1),variable="b_div_bmsy"))[c(1:4,6:8)]
```


```{r}
ggplot(subset(dat,variable=="b"))+ 
  geom_ribbon(aes(year,ymax=upper,ymin=lower),fill="red",alpha=0.25)+
  geom_line(aes(year,mean),col="red")+
  geom_line(aes(year,b),data=jb)+
  facet_grid(sp~Model,scale="free")+
  xlab("Biomass")+ylab("Year")+
  theme_bw()
```

**Figure `r iFig=iFig+1; iFig`** Absolute trends in abundance for all stocks and methods (black line are the true values).


```{r}
ggplot(subset(dat,variable=="b"&Model=="Catch & Index"))+ 
  geom_ribbon(aes(year,ymax=upper,ymin=lower),fill="red",alpha=0.25)+
  geom_line(aes(year,mean),col="red")+
  geom_line(aes(year,b),data=jb)+
  facet_grid(sp~Model,scale="free")+
  xlab("Biomass")+ylab("Year")+
  theme_bw()
```

**Figure `r iFig=iFig+1; iFig`** Absolute trends estimated by SRA+ using catch and the perfect index of abundance.


```{r}
ggplot(subset(dat,variable=="b"&Model=="Catch & Index Error"))+ 
  geom_ribbon(aes(year,ymax=upper,ymin=lower),fill="red",alpha=0.25)+
  geom_line(aes(year,mean),col="red")+
  geom_line(aes(year,b),data=jb)+
  facet_grid(sp~Model,scale="free")+
  xlab("Biomass")+ylab("Year")+
  theme_bw()
```

**Figure `r iFig=iFig+1; iFig`** Absolute trends: estimated by SRA+ using catch and the index of abundance with a CV of 40%.


```{r}
ggplot(subset(dat,variable=="b"&Model=="Catch & Heuristics"))+ 
  geom_ribbon(aes(year,ymax=upper,ymin=lower),fill="red",alpha=0.25)+
  geom_line(aes(year,mean),col="red")+
  geom_line(aes(year,b),data=jb)+
  facet_grid(sp~Model,scale="free")+
  xlab("Biomass")+ylab("Year")+
  theme_bw()
```

**Figure `r iFig=iFig+1; iFig`** Absolute trends: estimated by SRA+ using catch only and heuristics.


```{r}
ggplot(subset(dat,variable=="b"&Model=="Catch & Priors"))+ 
  geom_ribbon(aes(year,ymax=upper,ymin=lower),fill="red",alpha=0.25)+
  geom_line(aes(year,mean),col="red")+
  geom_line(aes(year,b),data=jb)+
  facet_grid(sp~Model,scale="free")+
  xlab("Biomass")+ylab("Year")+
  theme_bw()
```

**Figure `r iFig=iFig+1; iFig`** Absolute trends: estimated by SRA+ using catch only and priors for r, k and p.


```{r}
ggplot(subset(dat,variable=="b"&Model=="CMSY"))+ 
  geom_ribbon(aes(year,ymax=upper,ymin=lower),fill="red",alpha=0.25)+
  geom_line(aes(year,mean),col="red")+
  geom_line(aes(year,b),data=jb)+
  facet_grid(sp~Model,scale="free")+
  xlab("Biomass")+ylab("Year")+
  theme_bw()
```

**Figure `r iFig=iFig+1; iFig`** Absolute trends: estiimated by catchmsy.

```{r}
ggplot(subset(dat,variable=="b_div_bmsy"))+ 
  geom_hline(aes(yintercept=1))+
  geom_ribbon(aes(year,ymax=upper,ymin=lower),fill="red",alpha=0.25)+
  geom_line(aes(year,mean),col="red")+
  geom_line(aes(year,b_div_bmsy),data=jb)+
  facet_grid(sp~Model,scale="free")+
  xlab(expression(B:B[MSY]))+ylab("Year")+
  theme_bw()
```

**Figure `r iFig=iFig+1; iFig`** Trends relative to $B/B_{MSY}$ 

